Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-06-09 Codes/PrepareResults.rmd

set_flextable_defaults(
  font.family = "Times New Roman"
)
```

@@

```{r, dependson = "setup"}
# === subplot-level === #
vis_yield_subplot <-
  ggplot(field_subplot_sf) +
  geom_sf(aes(fill = yield), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "Yield level\n  (kg/ha)") +
  ggtitle("(2) Simulated yield level") +
  theme_figure
```

@@

@@

# === Summary Table (Training Data sets) === #
report_table_optN_train <-
  table_optN_prep %>%
  .[type == "train", !"type"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  # add_row(.after = 4) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # autofit() %>%
  # width(j = c(2,5,8,11), width=0.3) %>%
  # fix_border_issues()
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)

@@

```{r, dependson = "source-results"}
# === Summary Table (Testing Data sets) === #
report_table_optN <-
  table_optN_prep %>%
  .[type == "test", !"type"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  # add_row(.after = 4) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # autofit() %>%
  # width(j = c(2,5,8,11), width=0.3) %>%
  # fix_border_issues()
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```

@@

# === Summary Table (Testing Data sets) === #
table_optN_low_high <-
  table_optN_prep_low_high %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable() %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Degree = "Error Size",
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(4:5, 7:8, 10:11, 13:14), part = "header") %>%
  add_header(
    Degree = "",
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(5, 8, 11, 14), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  width(j = c(2, 5, 8, 11, 14), width = 0.3) %>%
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(4, 7, 10, 13), width = 0.6) %>%
  width(j = c(5, 8, 11, 14), width = 0.5) %>%
  width(j = 2, width = 0.7) %>%
  align(j = 2, align = "left", part = "body") %>%
  width(j = c(3, 6, 9, 12), width = 0.05)
```

>>>>

set_flextable_defaults(
  font.family = "Times New Roman"
  # font.family = "Cambria Math"
)
```

@@

```{r, dependson = "setup"}
# === subplot-level === #
vis_yield_subplot <-
  ggplot(field_subplot_sf) +
  geom_sf(aes(fill = yield), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "Yield level\n  (kg/ha)") +
  ggtitle("(2) Simulated yield level") +
  theme_figure

vis_yield_cell <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = yield), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "Yield level\n  (kg/ha)") +
  ggtitle("(2) Simulated yield level") +
  theme_figure
```

@@

```{r}

@@

# === Summary Table (Training Data sets) === #
pi_symb <- as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))
pi_symb[[1]]$font.family <- "Cambria Math"

report_table_optN_train <-
  table_optN_prep %>%
  .[type == "train", !"type"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  # add_row(.after = 4) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  # compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  # font(i = 2, j = c(4, 7, 10, 13), fontname = "Cambria Math", part = "header") %>%
  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = pi_symb) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # width(j = c(2,5,8,11), width=0.3) %>%
  # --- footer --- #
  add_footer_lines(values = "") %>%
  compose(value = as_paragraph("Note: "), part = "footer") %>%
  footnote(part = "body", ref_symbols = NA, inline = T, sep = "",
    value = pi_symb
  ) %>%
  footnote(part = "body", ref_symbols = NA, sep = "", inline = T,
    value = as_paragraph(" indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), ".")
  ) %>%
  # footnote(
  #   value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
  #   ref_symbols = NA
  # ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)

@@

```{r, dependson = "source-results"}
# === Summary Table (Testing Data sets) === #
pi_symb <- as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))
pi_symb[[1]]$font.family <- "Cambria Math"

report_table_optN <-
  table_optN_prep %>%
  .[type == "test", !"type"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  # add_row(.after = 4) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  # compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  # font(i = 2, j = c(4, 7, 10, 13), fontname = "Cambria Math", part = "header") %>%
  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = pi_symb) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # --- footer --- #
  add_footer_lines(values = "") %>%
  compose(value = as_paragraph("Note: "), part = "footer") %>%
  footnote(part = "body", ref_symbols = NA, inline = T, sep = "",
    value = pi_symb
  ) %>%
  footnote(part = "body", ref_symbols = NA, sep = "", inline = T,
    value = as_paragraph(" indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), ".")
  ) %>%
  # footnote(
  #   # i = 1, j = c(4, 7, 10, 13), part = "header",
  #   value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
  #   ref_symbols = NA
  # ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```

@@

# === Summary Table (Testing Data sets) === #
pi_symb <- as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))
pi_symb[[1]]$font.family <- "Cambria Math"

table_optN_low_high <-
  table_optN_prep_low_high %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable() %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Degree = "Error Size",
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(4:5, 7:8, 10:11, 13:14), part = "header") %>%
  add_header(
    Degree = "",
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  # compose(i = 2, j = c(5, 8, 11, 14), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  # font(i = 2, j = c(5, 8, 11, 14), fontname = "Cambria Math", part = "header") %>%
  compose(i = 2, j = c(5, 8, 11, 14), part = "header", value = pi_symb) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  width(j = c(2, 5, 8, 11, 14), width = 0.3) %>%
  # --- footer --- #
  add_footer_lines(values = "") %>%
  compose(value = as_paragraph("Note: "), part = "footer") %>%
  footnote(part = "body", ref_symbols = NA, inline = T, sep = "",
    value = pi_symb
  ) %>%
  footnote(part = "body", ref_symbols = NA, sep = "", inline = T,
    value = as_paragraph(" indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), ".")
  ) %>%
  # footnote(
  #   # i = 1, j = c(4, 7, 10, 13), part = "header",
  #   value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
  #   ref_symbols = NA
  # ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(4, 7, 10, 13), width = 0.6) %>%
  width(j = c(5, 8, 11, 14), width = 0.5) %>%
  width(j = 2, width = 0.7) %>%
  align(j = 2, align = "left", part = "body") %>%
  width(j = c(3, 6, 9, 12), width = 0.05)

# flextable(head(iris)) %>%
#   autofit() %>%
#   add_footer_lines(values = "") %>%
#   compose(value = as_paragraph("Note: "), part = "footer") %>%
#   footnote(part = "body", ref_symbols = NA, inline = T, sep = "",
#     value = pi_symb
#     ) %>%
#   footnote(part = "body", ref_symbols = NA, sep = "", inline = T,
#     value = as_paragraph(" indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), ".")
#     )
```

### 2022-06-09 Writing/CEA_final_submission/CoverLetter.rmd

---
title: ""
author: Shunkei Kakimoto
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
    # reference_docx: word_template_format.docx
    # pandoc_args: ["-Fpandoc-crossref"]
---

>>>>

---
title: ""
author: Shunkei Kakimoto
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: ../word_template.docx
---

### 2022-06-09 Writing/CEA_final_submission/Highlights.rmd

---
title: "Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation"
author: Shunkei Kakimoto, Taro Mieno, Takashi S. T. Tanaka, and David S. Bullock
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
    # reference_docx: word_template_format.docx
    # pandoc_args: ["-Fpandoc-crossref"]
bibliography: ML_VRA.bib
csl: computers-and-electronics-in-agriculture.csl
eqnPrefix: 
      - "Eq"
---

>>>>

---
title: "Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation"
author: Shunkei Kakimoto, Taro Mieno, Takashi S. T. Tanaka, and David S. Bullock
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: ../word_template.docx
---

### 2022-06-09 Writing/appendix.rmd

## Appendix A: Causal Tree Example {-}
Figure A.1 shows an example of a CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$) ($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.

>>>>

## Appendix A: Causal Tree Example {-}
Figure A.1 shows an example of a CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with electrical conductivity ($\textit{ecs}$) ($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment.
